Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-19 manuscript.tex
added acknowledgement

We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.

%-----------------------------------------------------------------------------------------------------------------------------------------------
%\section{Appendix}
\appendix
\section{Appendix} \label{appendix}

>>>>

We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
JCK was partially supported by the National Science Foundation under Grant AST 1616086 and by the National Aeronautics and Space Administration under grant 80NSSC18K0443.
\jessi{[Umberto - did you use the Yale HPC at any point during this project?  If so, we should add something like the following:] We also thank the Yale Center for Research Computing for the resources used to carryout this work.}
%-----------------------------------------------------------------------------------------------------------------------------------------------
%\section{Appendix}
\appendix
\section{Appendix} \label{appendix}
